Equalizer\\Programming and User Guide

### 2011-03-25 Developer/ProgrammingGuide/paper.tex
delete empty dir
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[x] Cleanup
[ ] Optimization
[ ] Documentation
Programming Guide: Minor revision
[ ] May break build
[ ] May break existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8 for Equalizer 1.0 \\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    \hline
  \end{tabularx}}
\clearpage

@@

The main function starts off with initializing the Equalizer library. The
command line arguments are passed on to Equalizer. The are used to set certain
default values based on Equalizer-specific options\footnote{Equalizer-specific
  options always start with -\,-eq-}, e.g., the default server
address. Furthermore, a \textsf{NodeFactory} is provided. The \textsf{EQERROR}
macro, and its counterparts \textsf{EQWARN}, \textsf{EQINFO} and \textsf{EQVERB}
allow selective debugging outputs with various logging levels:

@@

A static distributed object has to implement \textsf{getInstanceData}
and \textsf{applyInstanceData} to serialize and deserialize the object's
distributed data. These method provide an output or input stream as a
parameter, which abstracts the data transmission and can be used like a
\textsf{std::stream}.

@@

An \textsf{co::ConnectionSet} is used to manage multiple connections. The
typical use case is to have one or more listening connections for the local
process, and a number of connected connections for communicating with other
processes.

@@

A remote \textsf{Node} can be either be connected explicitly be the application
or due to a connection from the given remote node. The explicit connection can
be done by programmatically creating a node, adding the necessary
\textsf{ConnectionDescription}s and connecting it to the local node. It may also
be done by connecting the remote node to the local node by using its
\textsf{NodeID}. This will cause Collage to query connection information for
this node from the already-connected nodes, instantiating the node and
connecting it. Both operations may fail.

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netNode.pdf}
  {\caption{\label{fNetNode}Communication between two Nodes}}
\end{wrapfigure}
\fig{fNetNode} shows the communication between two nodes. The nodes in
the listening state also have a listening connection, which is not shown
in the Figure for complexity reasons.

@@

\if 0
{\footnotesize\begin{lstlisting}
\end{lstlisting}}
\fi

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8.1 for Equalizer 1.0 \\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.8.1   & Mar 25, 2011 & Minor Revision\\
    \hline
  \end{tabularx}}
\clearpage

@@

The main function starts off with initializing the Equalizer library. The
command line arguments are passed on to Equalizer. They are used to set certain
default values based on Equalizer-specific options\footnote{Equalizer-specific
  options always start with -\,-eq-}, e.g., the default server
address. Furthermore, a \textsf{NodeFactory} is provided. The \textsf{EQERROR}
macro, and its counterparts \textsf{EQWARN}, \textsf{EQINFO} and \textsf{EQVERB}
allow selective debugging outputs with various logging levels:

@@

A static distributed object has to implement \textsf{getInstanceData}
and \textsf{applyInstanceData} to serialize and deserialize the object's
distributed data. These methods provide an output or input stream as a
parameter, which abstracts the data transmission and can be used like a
\textsf{std::stream}.

@@

A \textsf{co::ConnectionSet} is used to manage multiple connections. The
typical use case is to have one or more listening connections for the local
process, and a number of connected connections for communicating with other
processes.

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netNode.pdf}
  {\caption{\label{fNetNode}Communication between two Nodes}}
\end{wrapfigure}
A remote \textsf{Node} can either be connected explicitly by the application or
due to a connection from the given remote node. The explicit connection can be
done by programmatically creating a node, adding the necessary
\textsf{ConnectionDescription}s and connecting it to the local node. It may also
be done by connecting the remote node to the local node by using its
\textsf{NodeID}. This will cause Collage to query connection information for
this node from the already-connected nodes, instantiating the node and
connecting it. Both operations may fail.

\fig{fNetNode} shows the communication between two nodes. The nodes in
the listening state also have a listening connection, which is not shown
in the Figure for complexity reasons.

@@
